[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-08 README/step_by_step_instructions.tex
Explained in README the change in the analysis time of Hybrid RaML

This table supports the two key claims in our paper (Section~7).
%
Firstly, \BayesWC{} and \BayesPC{} have higher percentages of sound cost bounds
than \Opt{} (in both data-driven and hybrid resource analysis).
%
Secondly, hybrid resource analysis (Hybrid \BayesWC{} and Hybrid \BayesPC{}) has
higher percentages of sound cost bounds than purely data-driven resource
analysis (Data-Driven \BayesWC{} and Data-Driven \BayesPC{}).

@@

>>>>

This table supports the two key claims in our paper (Section~7).
%
Firstly, in both data-driven and hybrid resource analysis, \BayesWC{} and
\BayesPC{} have higher percentages of sound cost bounds than \Opt{}.
%
Secondly, hybrid resource analysis (Hybrid \BayesWC{} and Hybrid \BayesPC{}) has
higher percentages of sound cost bounds than purely data-driven resource
analysis (Data-Driven \BayesWC{} and Data-Driven \BayesPC{}).

@@

The table of analysis time produced by the artifact looks different from the one
in the submitted version of the paper, in terms of both the numbers and layout.
%
This is because, since the submission, we have changed the configuration of
sampling-based Bayesian inference algorithms and rerun experiments.
%
In the camera ready version of the paper, we will update the analysis time in
Table~1.
